\scriptsize

\begin{landscape}

\renewcommand{\arraystretch}{1}
\begin{longtable}{|c|L{8cm}|L{14cm}|}
\hline 
\rowcolor{lightgray}
\# & \multicolumn{1}{c|}{Title} & \multicolumn{1}{c|}{Articles} \\
\hline \hline 
0 
& 
Miscellaneous (Colonial, Acciona, Amadeus, Grifols, Endesa, IAG, Bankinter...)
& 
$~\bullet~$ Colonial prevé ingresos por rentas de EUR338m en 2020

$~\bullet~$ Ventas de activos de Acciona le permitirán crecer en renovables

$~\bullet~$ Sabadell recomienda vender acción Amadeus por peor previsión ventas.
\\ \hline 
1
& 
Quarterly \& Semi-Annual Earnings Reports
& 
$~\bullet~$ Beneficio neto de Enagás 1s cae 9,8\% por menos ingresos y extraordinarios.

$~\bullet~$ Iberdrola: Beneficio neto de EUR1.025m en 1t

$~\bullet~$ Santander casi quintuplica beneficio 1t por ausencia de provisiones Covid.
\\ \hline 
2
& 
BBVA \& Sabadell: Financial Performance \& Strategic Movements
& 
$~\bullet~$ Subida de tipos en Turquía favorece margen de intereses de BBVA

$~\bullet~$ Sabadell reorganiza negocio en España tras llegada de nuevo CEO.

$~\bullet~$ Fitch rebaja un escalón la calificación de Banco Sabadell a aprobado bajo.
\\ \hline 
3
& 
Telefónica \& Cellnex: Telecommunications Tower Sales \& Market Dynamics
& 
$~\bullet~$ Acción Telefónica se dispara tras vender torres de filial en Europa y Latinoamérica.

$~\bullet~$ Telefónica encarga a Goldman Sachs vender su negocio de torres británico

$~\bullet~$ Competencia Países Bajos autoriza a Cellnex integrar 3.150 torres de Deutsche Telekom.
\\ \hline 
4
& 
CaixaBank: Mergers and Strategic Moves in the Banking Sector
& 
$~\bullet~$ CaixaBank y Bankia aprueban su proyecto de fusión

$~\bullet~$ CaixaBank cierra su primera emisión en libras de bonos verdes por 500 millones

$~\bullet~$ Fusión CaixaBank-Bankia podría generar ahorros de EUR500m
\\ \hline 
5
& 
Telefónica, Indra, \& MásMóvil: Regulatory and Strategic Moves in Telecom
& 
$~\bullet~$ Indra será socio de Telefónica en el despliegue de fibra óptica en Alemania.

$~\bullet~$ Telefónica lanza una oferta de recompra de sus bonos híbridos de EUR1.000m.

$~\bullet~$ UE deriva acuerdo de Liberty Global y Telefónica a regulador británico
\\ \hline 
6
& 
Siemens Gamesa: Supply Agreements, Profitability Targets in Renewable Energy
& 
$~\bullet~$ Siemens Gamesa suministrará turbinas a parque eólico de 150 MW de Elawan en España.

$~\bullet~$ Siemens Gamesa reduce su objetivo de rentabilidad para 2021.

$~\bullet~$ Siemens Gamesa suministrará 160 MW para mayor parque eólico de Filipinas.
\\ \hline 
7
& 
Cellnex: Strategic Acquisitions and Financial Moves in Telecom Infrastructure
& 
$~\bullet~$ Cellnex lanza una emisión de deuda de EUR1.850m

$~\bullet~$ Cellnex acuerda comprar 10.500 torres telecomunicaciones en Francia por EUR5.200m

$~\bullet~$ Familia Benetton vende 2,5\% de Cellnex al fondo soberano de Singapur
\\ \hline 
8
& 
Acciona, Endesa, Enagás \& Naturgy: Strategic Moves \& Regulatory Developments in the Energy Sector
& 
$~\bullet~$ Naturgy y Enagás estudian proyecto para producir hidrógeno verde en Asturias

$~\bullet~$ Ruptura de lazos de Argelia y Marruecos puede dañar el flujo de gas a España

$~\bullet~$ Acciona: Salida a bolsa de negocio de energía marcha según lo previsto para el 1s
\\ \hline 
9
& 
Repsol: Strategic Moves and Challenges in the Energy Sector
& 
$~\bullet~$ Repsol producirá hidrógeno verde en refinería vasca de Petronor en 2022

$~\bullet~$ Repsol y Talgo impulsarán conjuntamente creación de trenes de hidrógeno renovable

$~\bullet~$ Repsol accede a cartera de activos renovables en Chile mediante sociedad conjunta
\\ \hline 
10
& 
Ferrovial, Acciona: Strategic Expansions and Financial Maneuvers in Infrastructure
& 
$~\bullet~$ Ferrovial cierra la venta de Broadspectrum a Ventia por EUR291m

$~\bullet~$ Acciona se adjudica construcción de 2 carreteras en Polonia por EUR642m

$~\bullet~$ Renfe adjudica el contrato de servicios a bordo a Ferrovial por EUR272 millones
\\ \hline 
11
& 
Solaria: Strategic Moves and Market Challenges in Renewable Energy
& 
$~\bullet~$ Solaria invierte EUR220m en el mayor parque fotovoltaico de Europa.

$~\bullet~$ Solaria suministrará energía a Shell y Axpo con mayor planta fotovoltaica de Europa

$~\bullet~$ Goldman Sachs baja recomendación de Solaria tras alza de acción.
\\ \hline 
12
& 
Iberdrola: Strategic Collaborations and Renewable Energy Developments
& 
$~\bullet~$ Iberdrola construirá planta de autoconsumo para fábrica de Lactalis en España.

$~\bullet~$ Iberdrola y Mapfre lanzan vehículo de coinversión en renovables en España.

$~\bullet~$ Iberdrola se alía con Mitsubishi para descarbonizar la industria.
\\ \hline 
13
& 
IAG: Financial Performance
& 
$~\bullet~$ Resultados 3t de IAG son peores de lo esperado

$~\bullet~$ IAG consume liquidez más rápido de lo previsto

$~\bullet~$ Acción de IAG podría estar descontando segunda ampliación de capital
\\ \hline 
14
& 
Santander \& CaixaBank: Financial Moves and Sustainability Initiatives 
& 
$~\bullet~$ CaixaBank moviliza EUR12.000m en financiación sostenible en 9 primeros meses 2020.

$~\bullet~$ BEI y Banco Santander inyectarán EUR587 millones a pymes portuguesas.

$~\bullet~$ Banco Santander, líder en financiación de proyectos renovables en 2020.
\\ \hline 
15
& 
ACS \& Acciona: Strategic Movements and Infrastructure Projects
& 
$~\bullet~$ ACS y Acciona logran obras para nuevo aeropuerto australiano por EUR164m.

$~\bullet~$ Acciona se adjudica 3 contratos para operar depuradoras en Cerdeña por EUR210m.

$~\bullet~$ ACS prevé que beneficio neto crezca en torno al 30\% en 2021
\\ \hline 
16
& 
Telefónica: Financial Performance and Strategic Moves
& 
$~\bullet~$ Reducción deuda de Telefónica mejorará percepción de analistas

$~\bullet~$ Beneficio Telefónica crece más del doble en 1t por menos gastos financieros.

$~\bullet~$ Telefónica, América Móvil y TIM compran la red móvil de la brasileña Oi.
\\ \hline 
17
& 
Meliá and Spanish Tourism Sector: Challenges Amidst the Pandemic
& 
$~\bullet~$ Meliá: Sector hotelero español afronta con un cauto optimismo otro verano incierto.

$~\bullet~$ Meliá reclama al Gobierno español EUR116m por daños causados por pandemia.

$~\bullet~$ Meliá: Confinamientos locales por Covid-19 seguirán afectando a Meliá.
\\ \hline 
18
& 
Takeover Bids for Naturgy and MásMóvil
& 
$~\bullet~$ Fondo australiano IFM lanza oferta de EUR5.000m por 22,69\% de Naturgy.

$~\bullet~$ Fondo Polygon solicita a CNMV que analice y altere la opa por MásMóvil.

$~\bullet~$ IFM acepta condiciones de Gobierno español en opa parcial por Naturgy.
\\ \hline 
19
& 
Naturgy: Financial Performance
& 
$~\bullet~$ Naturgy presenta unos resultados de 2020 "débiles"

$~\bullet~$ Naturgy podría revisar al alza su plan estratégico por precios del gas.

$~\bullet~$ Bank of America prevé potencial alcista para Naturgy por fundamentales.
\\ \hline 
20
& 
PharmaMar, Grifols: Regulatory Approvals and Market Moves in the Pharmaceutical Sector
& 
$~\bullet~$ Tribunal UE anula negativa de Comisión Europea a comercializar fármaco de PharmaMar.

$~\bullet~$ Grifols inicia emisión de bonos por EUR2.000m para compra de Biotest.

$~\bullet~$ PharmaMar anuncia aprobación de lurbinectedina para cáncer de pulmón en Australia.
\\ \hline 
21
& 
Repsol: Financial Performance
& 
$~\bullet~$ Repsol: Pérdida neta de EUR3.289m en 2020.

$~\bullet~$ Repsol registra pérdidas de EUR711m en 4t por provisiones en exploración y producción

$~\bullet~$ Repsol pasa a pérdidas de EUR94m en 3t por provisiones y menores márgenes refino.
\\ \hline 
22
& 
Aena: Financial Performance
& 
$~\bullet~$ JPMorgan eleva precio objetivo de Aena a EUR155 desde EUR135.

$~\bullet~$ Aena se juega un recorte de ingresos de hasta EUR2.000m por alquileres.

$~\bullet~$ Aena pierde EUR170,7m en 1s tras hundirse tráfico de pasajeros por pandemia.
\\ \hline 
23
& 
Enagás, Endesa, Iberdrola, Red Eléctrica: Regulatory and Market Challenges in the Energy Sector
& 
$~\bullet~$ Eléctricas españolas seguirán bajo presión en bolsa 

$~\bullet~$ Medidas de Gobierno español son malas noticias para sector eléctrico.

$~\bullet~$ Precio electricidad España cierra febrero con descenso del 52\% vs enero
\\ \hline 
24
& 
BBVA, CaixaBank, Banco Sabadell: Layoffs and Restructuring
& 
$~\bullet~$ CaixaBank propone a sindicatos ERE que afecta a 8.291 empleados.

$~\bullet~$ Banco Santander cierra su ERE con 3.572 salidas voluntarias y 19 despidos 

$~\bullet~$ Sabadell prepara un plan de ajuste que afectará a 2.000 empleados
\\ \hline 
25
& 
Inditex, Acerinox: Market Performance and Strategic Developments in the Post-Covid Context
& 
$~\bullet~$ Inditex reabre 94\% de sus tiendas en todo el mundo tras pandemia Covid-19.

$~\bullet~$ Venta de Nippon Steel en Acerinox es negativa, pero se esperaba.

$~\bullet~$ Acción Inditex ya descuenta fuerte recuperación de negocio.
\\ \hline 
\end{longtable}
\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\scriptsize

\begin{landscape}

\renewcommand{\arraystretch}{1}
\begin{longtable}{|c|L{8cm}|L{14cm}|}
\hline 
\rowcolor{lightgray}
\# & \multicolumn{1}{c|}{Title} & \multicolumn{1}{c|}{Articles} \\
\hline \hline 
0 
& 
Miscellaneous (Colonial, Acciona, Amadeus, Grifols, Endesa, IAG, Bankinter...)
& 
$~\bullet~$ Colonial forecasts rental income of EUR338m in 2020

$~\bullet~$ Acciona's asset sales will allow it to grow in renewables

$~\bullet~$ Sabadell recommends selling Amadeus shares due to worse sales forecast.
\\ \hline 
1
& 
Quarterly \& Semi-Annual Earnings Reports
& 
$~\bullet~$ Enagás 1H net profit falls 9.8\% due to lower income and extraordinary items.

$~\bullet~$ Iberdrola: Net profit of EUR1.025m in Q1

$~\bullet~$ Santander almost quintuples Q1 profit due to absence of Covid provisions.
\\ \hline 
2
& 
BBVA \& Sabadell: Financial Performance \& Strategic Movements
& 
$~\bullet~$ Interest rate hike in Turkey favors BBVA's net interest margin

$~\bullet~$ Sabadell reorganizes business in Spain following the arrival of the new CEO.

$~\bullet~$ Fitch downgrades Banco Sabadell's rating one notch to low grade.
\\ \hline 
3
& 
Telefónica \& Cellnex: Telecommunications Tower Sales \& Market Dynamics
& 
$~\bullet~$ Telefónica shares soar after selling towers of its subsidiary in Europe and Latin America.

$~\bullet~$ Telefónica hires Goldman Sachs to sell its British tower business

$~\bullet~$ Dutch Competition Authority authorizes Cellnex to integrate 3,150 Deutsche Telekom towers.
\\ \hline 
4
& 
CaixaBank: Mergers and Strategic Moves in the Banking Sector
& 
$~\bullet~$ CaixaBank and Bankia approve their merger project

$~\bullet~$ CaixaBank closes its first issuance of green bonds in pounds for 500 million

$~\bullet~$ CaixaBank-Bankia merger could generate EUR500m in savings
\\ \hline 
5
& 
Telefónica, Indra, \& MásMóvil: Regulatory and Strategic Moves in Telecom
& 
$~\bullet~$ Indra to partner with Telefónica in the deployment of fiber optics in Germany.

$~\bullet~$ Telefónica launches a buyback offer for its hybrid bonds of EUR1.000m.

$~\bullet~$ EU refers Liberty Global and Telefónica agreement to UK regulator
\\ \hline 
6
& 
Siemens Gamesa: Supply Agreements, Profitability Targets in Renewable Energy
& 
$~\bullet~$ Siemens Gamesa will supply turbines to Elawan's 150 MW wind farm in Spain.

$~\bullet~$ Siemens Gamesa lowers its profitability target for 2021.

$~\bullet~$ Siemens Gamesa will supply 160 MW for the largest wind farm in the Philippines.
\\ \hline 
7
& 
Cellnex: Strategic Acquisitions and Financial Moves in Telecom Infrastructure
& 
$~\bullet~$ Cellnex launches a EUR1.850m debt issue

$~\bullet~$ Cellnex agrees to buy 10,500 telecommunications towers in France for EUR5.200m

$~\bullet~$ Benetton family sells 2.5\% of Cellnex to Singapore sovereign fund
\\ \hline 
8
& 
Acciona, Endesa, Enagás \& Naturgy: Strategic Moves \& Regulatory Developments in the Energy Sector
& 
$~\bullet~$ Naturgy and Enagás study project to produce green hydrogen in Asturias

$~\bullet~$ Break of ties between Algeria and Morocco may damage gas flow to Spain

$~\bullet~$ Acciona: Energy business IPO on track for 1H
\\ \hline 
9
& 
Repsol: Strategic Moves and Challenges in the Energy Sector
& 
$~\bullet~$ Repsol to produce green hydrogen at Petronor refinery in 2022

$~\bullet~$ Repsol and Talgo to jointly promote the creation of renewable hydrogen trains

$~\bullet~$ Repsol gains access to a portfolio of renewable assets in Chile through a joint venture
\\ \hline 
10
& 
Ferrovial, Acciona: Strategic Expansions and Financial Maneuvers in Infrastructure
& 
$~\bullet~$ Ferrovial closes the sale of Broadspectrum to Ventia for EUR291m

$~\bullet~$ Acciona awarded the construction of 2 roads in Poland for EUR642m

$~\bullet~$ Renfe awards on-board services contract to Ferrovial for EUR272m
\\ \hline 
11
& 
Solaria: Strategic Moves and Market Challenges in Renewable Energy
& 
$~\bullet~$ Solaria invests EUR220m in Europe's largest photovoltaic park.

$~\bullet~$ Solaria will supply energy to Shell and Axpo with Europe's largest photovoltaic plant

$~\bullet~$ Goldman Sachs downgrades Solaria recommendation after stock rise.
\\ \hline 
12
& 
Iberdrola: Strategic Collaborations and Renewable Energy Developments
& 
$~\bullet~$ Iberdrola will build a self-consumption plant for Lactalis factory in Spain.

$~\bullet~$ Iberdrola and Mapfre launch a renewable energy co-investment vehicle in Spain.

$~\bullet~$ Iberdrola partners with Mitsubishi to decarbonize the industry.
\\ \hline 
13
& 
IAG: Financial Performance
& 
$~\bullet~$ IAG Q3 results worse than expected

$~\bullet~$ IAG burns cash faster than anticipated

$~\bullet~$ IAG stock may be pricing in a second capital increase
\\ \hline 
14
& 
Santander \& CaixaBank: Financial Moves and Sustainability Initiatives 
& 
$~\bullet~$ CaixaBank mobilizes EUR12.000m in sustainable financing in the first 9 months of 2020.

$~\bullet~$ EIB and Banco Santander will inject EUR587m into Portuguese SMEs.

$~\bullet~$ Banco Santander, leader in renewable project financing in 2020.
\\ \hline 
15
& 
ACS \& Acciona: Strategic Movements and Infrastructure Projects
& 
$~\bullet~$ ACS and Acciona win contracts for new Australian airport worth EUR164m.

$~\bullet~$ Acciona awarded 3 contracts to operate wastewater treatment plants in Sardinia for EUR210m.

$~\bullet~$ ACS expects net profit to grow by around 30\% in 2021
\\ \hline 
16
& 
Telefónica: Financial Performance and Strategic Moves
& 
$~\bullet~$ Reduction in Telefónica's debt will improve analysts' perception

$~\bullet~$ Telefónica's profit more than doubles in Q1 due to lower financial expenses.

$~\bullet~$ Telefónica, América Móvil and TIM buy the mobile network of Brazil's Oi.
\\ \hline 
17
& 
Meliá and Spanish Tourism Sector: Challenges Amidst the Pandemic
& 
$~\bullet~$ Meliá: Spanish hotel sector faces another uncertain summer with cautious optimism.

$~\bullet~$ Meliá claims EUR116m from the Spanish government for pandemic-related damages.

$~\bullet~$ Meliá: Local Covid-19 lockdowns will continue to affect Meliá.
\\ \hline 
18
& 
Takeover Bids for Naturgy and MásMóvil
& 
$~\bullet~$ Australian fund IFM launches EUR5.000m bid for 22.69\% of Naturgy.

$~\bullet~$ Polygon fund asks CNMV to review and alter the bid for MásMóvil.

$~\bullet~$ IFM accepts Spanish government conditions in partial bid for Naturgy.
\\ \hline 
19
& 
Naturgy: Financial Performance
& 
$~\bullet~$ Naturgy presents "weak" 2020 results

$~\bullet~$ Naturgy may revise its strategic plan upwards due to gas prices.

$~\bullet~$ Bank of America sees upside potential for Naturgy based on fundamentals.
\\ \hline 
20
& 
PharmaMar, Grifols: Regulatory Approvals and Market Moves in the Pharmaceutical Sector
& 
$~\bullet~$ EU court annuls European Commission's refusal to market PharmaMar drug.

$~\bullet~$ Grifols starts issuing EUR2.000m bonds to buy Biotest.

$~\bullet~$ PharmaMar announces approval of lurbinectedin for lung cancer in Australia.
\\ \hline 
21
& 
Repsol: Financial Performance
& 
$~\bullet~$ Repsol: Net loss of EUR3.289m in 2020.

$~\bullet~$ Repsol reports a loss of EUR711m in Q4 due to exploration and production provisions

$~\bullet~$ Repsol posts a loss of EUR94m in Q3 due to provisions and lower refining margins.
\\ \hline 
22
& 
Aena: Financial Performance
& 
$~\bullet~$ JPMorgan raises Aena's target price to EUR155 from EUR135.

$~\bullet~$ Aena risks a revenue cut of up to EUR2.000m due to rents.

$~\bullet~$ Aena loses EUR170.7m in 1H as passenger traffic plummets due to the pandemic.
\\ \hline 
23
& 
Enagás, Endesa, Iberdrola, Red Eléctrica: Regulatory and Market Challenges in the Energy Sector
& 
$~\bullet~$ Spanish electric utilities will remain under pressure in the stock market 

$~\bullet~$ Spanish government measures are bad news for the electric sector.

$~\bullet~$ Spain's electricity price closes February with a 52\% drop vs January
\\ \hline 
24
& 
BBVA, CaixaBank, Banco Sabadell: Layoffs and Restructuring
& 
$~\bullet~$ CaixaBank proposes to unions a redundancy plan affecting 8,291 employees.

$~\bullet~$ Banco Santander closes its redundancy plan with 3,572 voluntary exits and 19 dismissals 

$~\bullet~$ Sabadell prepares an adjustment plan affecting 2,000 employees
\\ \hline 
25
& 
Inditex, Acerinox: Market Performance and Strategic Developments in the Post-Covid Context
& 
$~\bullet~$ Inditex reopens 94\% of its stores worldwide after Covid-19 pandemic.

$~\bullet~$ Sale of Nippon Steel in Acerinox is negative, but expected.

$~\bullet~$ Inditex stock already prices in a strong business recovery.
\\ \hline 
\end{longtable}
\end{landscape}
