\section{Introduction}

\subsection{Background}
Asset pricing is a cornerstone of financial economics, providing the theoretical and empirical foundation for understanding how assets are valued in financial markets. Traditional asset pricing models, such as the Capital Asset Pricing Model (CAPM) \cite{Sharpe1964}, the Arbitrage Pricing Theory (APT) \cite{Ross1976}, and the Fama-French three-factor model \cite{Fama1993}, have been instrumental in explaining the relationship between risk and expected returns. These models typically rely on linear relationships and predefined risk factors to estimate asset prices and returns.

On the other hand, the Synthetic Control Method (SCM) \cite{Abadie2010} is an econometric technique originally developed for causal inference in comparative case studies. SCM constructs a synthetic counterpart for a treated unit by optimally weighting a combination of control units, thereby allowing for a counterfactual analysis of the treated unit's performance in the absence of the intervention. While SCM has been predominantly applied in policy evaluation and program assessment, its methodological framework offers promising avenues for addressing complexities in asset pricing that traditional models may not fully capture.

\subsection{Motivation}
Despite the successes of traditional asset pricing models, they often face limitations in capturing nonlinear relationships, structural breaks, and heterogeneous effects across different market conditions. These challenges can lead to model misspecification and biased estimates of asset returns and risk premia. The Synthetic Control Method, with its flexible and data-driven approach to constructing counterfactuals, presents a potential solution to these limitations.

Integrating SCM into asset pricing can enhance the ability to model complex market dynamics by allowing for the creation of synthetic portfolios that better reflect the underlying economic conditions. This integration can improve the estimation of asset prices, enhance risk assessment, and provide more robust tools for portfolio management and financial decision-making. Furthermore, SCM's capacity to handle high-dimensional data and its non-parametric nature align well with the evolving landscape of financial markets characterized by increased data availability and complexity.

\subsection{Objectives}
The primary objective of this paper is to develop a theoretical framework that integrates the Synthetic Control Method into asset pricing models. Specifically, the paper aims to:

\begin{enumerate}
    \item \textbf{Develop the Theoretical Foundations:} Establish the mathematical underpinnings of applying SCM within the context of asset pricing, including the construction of synthetic portfolios and the derivation of key properties.
    \item \textbf{Enhance Model Flexibility:} Demonstrate how SCM can address limitations of traditional asset pricing models by capturing nonlinear relationships and accommodating structural changes in the market.
    \item \textbf{Compare with Traditional Models:} Provide a comparative analysis between the SCM-based approach and conventional asset pricing models to highlight the advantages and potential improvements in estimation accuracy and robustness.
    \item \textbf{Outline Potential Applications:} Explore theoretical applications of the SCM-based asset pricing model in areas such as risk management, portfolio optimization, and the evaluation of market interventions.
\end{enumerate}

\subsection{Structure of the Paper}
The paper is organized as follows:

\begin{itemize}
    \item \textbf{Section 2: Literature Review} \\
    Reviews existing asset pricing models and the Synthetic Control Method, highlighting the intersection of these two areas and identifying gaps in the current literature.
    
    \item \textbf{Section 3: Theoretical Framework} \\
    Presents the mathematical foundations of SCM and details the integration of SCM into asset pricing models, including key variables, parameters, and assumptions.
    
    \item \textbf{Section 4: Theoretical Developments} \\
    Delves into the construction of synthetic portfolios, derives essential properties and theorems, and conducts a comparative analysis with traditional asset pricing approaches.
    
    \item \textbf{Section 5: Applications and Implications} \\
    Discusses the implementation of the SCM-based asset pricing model, outlines potential case studies, and explores the implications for financial theory and practice.
    
    \item \textbf{Section 6: Discussion} \\
    Summarizes the strengths and limitations of the proposed approach and suggests directions for future research.
    
    \item \textbf{Section 7: Conclusion} \\
    Recaps the main contributions of the paper and underscores the significance of integrating SCM into asset pricing.
    
    \item \textbf{References} \\
    Lists all the academic works cited throughout the paper.
    
    \item \textbf{Appendices} \\
    Provides supplementary mathematical derivations and proofs that support the main text.
\end{itemize}

By systematically developing the theoretical integration of the Synthetic Control Method into asset pricing, this paper seeks to contribute to the advancement of financial modeling techniques, offering enhanced tools for analysts and researchers in the field.

\bibliographystyle{apalike}
\bibliography{references}

\input{txt_literature.tex}
\input{txt_theory.tex}
\input{txt_developments.tex}




