%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%% 		ENGLISH 		%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{landscape}
\renewcommand{\arraystretch}{1}

%\scriptsize
{\fontsize{9}{9}\selectfont % Set custom font size between \scriptsize and \tiny

%----------------------------------------------------
\begin{longtable}{|c|L{8cm}|L{14cm}|}
\caption{KMeans clustering. Proposed name for the clusters and sample of 3 articles for each cluster.} % Caption for the longtable
\label{tab:KMeans_Articles_3_English} \\
\hline 
\rowcolor{lightgray}
\# & \multicolumn{1}{c|}{Title} & \multicolumn{1}{c|}{Articles} \\
\hline \hline 
0 
& 
Miscellaneous (Colonial, Acciona, Amadeus, Grifols, Endesa, IAG, Bankinter...)
& 
\textbullet~Colonial forecasts rental income of EUR338m in 2020

\textbullet~Acciona's asset sales will allow it to grow in renewables

\textbullet~Sabadell recommends selling Amadeus shares due to worse sales forecast.
\\ \hline 
1
& 
Quarterly \& Semi-Annual Earnings Reports
& 
\textbullet~Enagás 1H net profit falls 9.8\% due to lower income and extraordinary items.

\textbullet~Iberdrola: Net profit of EUR1.025m in Q1

\textbullet~Santander almost quintuples Q1 profit due to absence of Covid provisions.
\\ \hline 
2
& 
BBVA \& Sabadell: Financial Performance \& Strategic Movements
& 
\textbullet~Interest rate hike in Turkey favors BBVA's net interest margin

\textbullet~Sabadell reorganizes business in Spain following the arrival of the new CEO.

\textbullet~Fitch downgrades Banco Sabadell's rating one notch to low grade.
\\ \hline 
3
& 
Telefónica \& Cellnex: Telecommunications Tower Sales \& Market Dynamics
& 
\textbullet~Telefónica shares soar after selling towers of its subsidiary in Europe and Latin America.

\textbullet~Telefónica hires Goldman Sachs to sell its British tower business

\textbullet~Dutch Competition Authority authorizes Cellnex to integrate 3,150 Deutsche Telekom towers.
\\ \hline 
4
& 
CaixaBank: Mergers and Strategic Moves in the Banking Sector
& 
\textbullet~CaixaBank and Bankia approve their merger project

\textbullet~CaixaBank closes its first issuance of green bonds in pounds for 500 million

\textbullet~CaixaBank-Bankia merger could generate EUR500m in savings
\\ \hline 
5
& 
Telefónica, Indra, \& MásMóvil: Regulatory and Strategic Moves in Telecom
& 
\textbullet~Indra to partner with Telefónica in the deployment of fiber optics in Germany.

\textbullet~Telefónica launches a buyback offer for its hybrid bonds of EUR1.000m.

\textbullet~EU refers Liberty Global and Telefónica agreement to UK regulator
\\ \hline 
6
& 
Siemens Gamesa: Supply Agreements, Profitability Targets in Renewable Energy
& 
\textbullet~Siemens Gamesa will supply turbines to Elawan's 150 MW wind farm in Spain.

\textbullet~Siemens Gamesa lowers its profitability target for 2021.

\textbullet~Siemens Gamesa will supply 160 MW for the largest wind farm in the Philippines.
\\ \hline 
7
& 
Cellnex: Strategic Acquisitions and Financial Moves in Telecom Infrastructure
& 
\textbullet~Cellnex launches a EUR1.850m debt issue

\textbullet~Cellnex agrees to buy 10,500 telecommunications towers in France for EUR5.200m

\textbullet~Benetton family sells 2.5\% of Cellnex to Singapore sovereign fund
\\ \hline 
8
& 
Acciona, Endesa, Enagás \& Naturgy: Strategic Moves \& Regulatory Developments in the Energy Sector
& 
\textbullet~Naturgy and Enagás study project to produce green hydrogen in Asturias

\textbullet~Break of ties between Algeria and Morocco may damage gas flow to Spain

\textbullet~Acciona: Energy business IPO on track for 1H
\\ \hline 
9
& 
Repsol: Strategic Moves and Challenges in the Energy Sector
& 
\textbullet~Repsol to produce green hydrogen at Petronor refinery in 2022

\textbullet~Repsol and Talgo to jointly promote the creation of renewable hydrogen trains

\textbullet~Repsol gains access to a portfolio of renewable assets in Chile through a joint venture
\\ \hline 
10
& 
Ferrovial, Acciona: Strategic Expansions and Financial Maneuvers in Infrastructure
& 
\textbullet~Ferrovial closes the sale of Broadspectrum to Ventia for EUR291m

\textbullet~Acciona awarded the construction of 2 roads in Poland for EUR642m

\textbullet~Renfe awards on-board services contract to Ferrovial for EUR272m
\\ \hline 
11
& 
Solaria: Strategic Moves and Market Challenges in Renewable Energy
& 
\textbullet~Solaria invests EUR220m in Europe's largest photovoltaic park.

\textbullet~Solaria will supply energy to Shell and Axpo with Europe's largest photovoltaic plant

\textbullet~Goldman Sachs downgrades Solaria recommendation after stock rise.
\\ \hline 
12
& 
Iberdrola: Strategic Collaborations and Renewable Energy Developments
& 
\textbullet~Iberdrola will build a self-consumption plant for Lactalis factory in Spain.

\textbullet~Iberdrola and Mapfre launch a renewable energy co-investment vehicle in Spain.

\textbullet~Iberdrola partners with Mitsubishi to decarbonize the industry.
\\ \hline 
13
& 
IAG: Financial Performance
& 
\textbullet~IAG Q3 results worse than expected

\textbullet~IAG burns cash faster than anticipated

\textbullet~IAG stock may be pricing in a second capital increase
\\ \hline 
14
& 
Santander \& CaixaBank: Financial Moves and Sustainability Initiatives 
& 
\textbullet~CaixaBank mobilizes EUR12.000m in sustainable financing in the first 9 months of 2020.

\textbullet~EIB and Banco Santander will inject EUR587m into Portuguese SMEs.

\textbullet~Banco Santander, leader in renewable project financing in 2020.
\\ \hline 
15
& 
ACS \& Acciona: Strategic Movements and Infrastructure Projects
& 
\textbullet~ACS and Acciona win contracts for new Australian airport worth EUR164m.

\textbullet~Acciona awarded 3 contracts to operate wastewater treatment plants in Sardinia for EUR210m.

\textbullet~ACS expects net profit to grow by around 30\% in 2021
\\ \hline 
16
& 
Telefónica: Financial Performance and Strategic Moves
& 
\textbullet~Reduction in Telefónica's debt will improve analysts' perception

\textbullet~Telefónica's profit more than doubles in Q1 due to lower financial expenses.

\textbullet~Telefónica, América Móvil and TIM buy the mobile network of Brazil's Oi.
\\ \hline 
17
& 
Meliá and Spanish Tourism Sector: Challenges Amidst the Pandemic
& 
\textbullet~Meliá: Spanish hotel sector faces another uncertain summer with cautious optimism.

\textbullet~Meliá claims EUR116m from the Spanish government for pandemic-related damages.

\textbullet~Meliá: Local Covid-19 lockdowns will continue to affect Meliá.
\\ \hline 
18
& 
Takeover Bids for Naturgy and MásMóvil
& 
\textbullet~Australian fund IFM launches EUR5.000m bid for 22.69\% of Naturgy.

\textbullet~Polygon fund asks CNMV to review and alter the bid for MásMóvil.

\textbullet~IFM accepts Spanish government conditions in partial bid for Naturgy.
\\ \hline 
19
& 
Naturgy: Financial Performance
& 
\textbullet~Naturgy presents "weak" 2020 results

\textbullet~Naturgy may revise its strategic plan upwards due to gas prices.

\textbullet~Bank of America sees upside potential for Naturgy based on fundamentals.
\\ \hline 
20
& 
PharmaMar, Grifols: Regulatory Approvals and Market Moves in the Pharmaceutical Sector
& 
\textbullet~EU court annuls European Commission's refusal to market PharmaMar drug.

\textbullet~Grifols starts issuing EUR2.000m bonds to buy Biotest.

\textbullet~PharmaMar announces approval of lurbinectedin for lung cancer in Australia.
\\ \hline 
21
& 
Repsol: Financial Performance
& 
\textbullet~Repsol: Net loss of EUR3.289m in 2020.

\textbullet~Repsol reports a loss of EUR711m in Q4 due to exploration and production provisions

\textbullet~Repsol posts a loss of EUR94m in Q3 due to provisions and lower refining margins.
\\ \hline 
22
& 
Aena: Financial Performance
& 
\textbullet~JPMorgan raises Aena's target price to EUR155 from EUR135.

\textbullet~Aena risks a revenue cut of up to EUR2.000m due to rents.

\textbullet~Aena loses EUR170.7m in 1H as passenger traffic plummets due to the pandemic.
\\ \hline 
23
& 
Enagás, Endesa, Iberdrola, Red Eléctrica: Regulatory and Market Challenges in the Energy Sector
& 
\textbullet~Spanish electric utilities will remain under pressure in the stock market 

\textbullet~Spanish government measures are bad news for the electric sector.

\textbullet~Spain's electricity price closes February with a 52\% drop vs January
\\ \hline 
24
& 
BBVA, CaixaBank, Banco Sabadell: Layoffs and Restructuring
& 
\textbullet~CaixaBank proposes to unions a redundancy plan affecting 8,291 employees.

\textbullet~Banco Santander closes its redundancy plan with 3,572 voluntary exits and 19 dismissals 

\textbullet~Sabadell prepares an adjustment plan affecting 2,000 employees
\\ \hline 
25
& 
Inditex, Acerinox: Market Performance and Strategic Developments in the Post-Covid Context
& 
\textbullet~Inditex reopens 94\% of its stores worldwide after Covid-19 pandemic.

\textbullet~Sale of Nippon Steel in Acerinox is negative, but expected.

\textbullet~Inditex stock already prices in a strong business recovery.
\\ \hline 
\end{longtable}
%----------------------------------------------------
}

\end{landscape}