%==============[	  Sonnet 3.5  ]==============

Pairs trading has emerged as a cornerstone of statistical arbitrage strategies, with a rich history in both academic research and practical applications. The foundational work of \cite{Gatev2006} provided the first comprehensive academic study of pairs trading, documenting significant excess returns of up to 11\% annually for self-financing portfolios over a 40-year period from 1962 to 2002. This seminal paper was complemented by the theoretical framework developed in \cite{Elliott2005}, which introduced a mean-reverting Gaussian Markov chain model for spread dynamics and established analytical methods for parameter estimation using the EM algorithm.

The cointegration approach to pairs trading has been extensively studied, beginning with the foundational work of \cite{vidyamurthy2004pairs}, which provided a comprehensive framework for implementing cointegration-based strategies. Subsequent research has explored various aspects of this approach: \cite{Caldeira2013} demonstrated the effectiveness of cointegration-based selection methods in the Brazilian market, while \cite{Huck2014} provided evidence that cointegration-based strategies outperform distance-based methods. \cite{Cartea2015} extended the framework by incorporating optimal dynamic investment strategies, and \cite{Lintilhac2016} applied these techniques to cryptocurrency markets.

Empirical investigations have thoroughly examined the profitability of pairs trading across different markets and time periods. \cite{Chen2019} decomposed trading signals into short-term reversal and pairs momentum components, while \cite{Do2010} documented a declining trend in profitability but noted strong performance during market turbulence. \cite{Bowen2014} provided comprehensive UK evidence, and \cite{Krauss2016} conducted an extensive review of different methodological approaches. \cite{Rad2016} compared distance, cointegration, and copula-based methods, finding varying degrees of success across different market conditions.

For readers seeking a deeper understanding of pairs trading methodologies, several didactic sources are available. \cite{hudsonthames2024} provides a comprehensive practical guide covering various approaches from basic implementation to advanced techniques. \cite{alexander2008market} offers valuable introductions to both cointegration analysis and copula applications in financial markets, particularly in chapters II.5 and II.6.

The application of copulas to pairs trading represents a significant methodological advancement. \cite{Min2010} introduced Bayesian inference for multivariate copulas using pair-copula constructions, while \cite{stander2013trading} and \cite{Liew2013} demonstrated the advantages of copula-based dependence modeling over traditional correlation measures. \cite{Xie2016} further developed these ideas, showing improved profitability compared to conventional methods. The framework was extended to multiple dimensions by \cite{lau2016multi}, while \cite{Krauss2017} incorporated sophisticated exit rules based on copula-derived signals. Dynamic extensions were introduced by \cite{zhi2017dynamic}, and applications to high-frequency data were explored by \cite{Chu2018}. Recent developments include the mixed copula approach of \cite{SabinodaSilva2023}, the Copula-GARCH model of \cite{Wang2023}, multivariate extensions by \cite{He2024}, and cryptocurrency applications by \cite{Tadi2025}.

Alternative approaches to pairs trading have emerged in recent years. \cite{do2006new} developed a stochastic residual spread model, while \cite{Zeng2014} focused on optimal threshold determination. Machine learning applications have gained prominence, with \cite{Sarmento2020} utilizing LSTM networks, \cite{Han2023} employing unsupervised learning for pair selection, and \cite{Roychoudhury2023} combining clustering with deep reinforcement learning. Novel optimization approaches include the convex-concave framework of \cite{Johansson2024}, the graphical matching approach of \cite{qureshi2024pairs}, and the clustering-based methodology of \cite{Rotondi2025}.

Our synthetic control methodology draws inspiration from the index tracking literature. \cite{Alexander1999} pioneered the application of cointegration to tracking problems, while \cite{Alexander2002} and \cite{Alexander2005a} developed enhanced indexing strategies. \cite{Alexander2005b} explored market regime effects, and recent work by \cite{Shu2020} introduced adaptive elastic net methods for high-dimensional tracking. \cite{Bradrania2021} incorporated machine learning for state-dependent stock selection, demonstrating the evolving sophistication of tracking methodologies.

%==============[	  o1  ]==============

%\section{Literature Review}
%
%\paragraph{Pairs Trading Classics.}
%Early foundational work on pairs trading can be traced to studies that pioneered the strategy's empirical validation and theoretical underpinnings. In particular, \cite{Gatev2006} proposed a simple yet effective framework in which stocks are paired according to minimized distance between normalized historical prices, thus generating substantial excess returns. Another key reference, \cite{Elliott2005}, introduced a mean-reverting Gaussian Markov chain model for the spread, providing one of the first analytical frameworks that bridges theory and practice in pairs trading.
%
%\paragraph{Cointegration-Based Approaches.}
%A popular way to identify and exploit persistent relationships in pairs trading has involved cointegration analysis. \cite{vidyamurthy2004pairs} stands out as a seminal reference, detailing how cointegration can be applied to detect mean-reverting spreads in equity markets. Subsequent work (e.g., \cite{Caldeira2013}, \cite{Huck2014}, \cite{Cartea2015}, \cite{Lintilhac2016}) consistently investigates how cointegration frameworks can isolate stable long-term relationships, offering systematic procedures for portfolio construction, parameter estimation, and risk management within the pairs trading context.
%
%\paragraph{Empirical Investigations of Pairs Trading.}
%Several studies have examined the profitability and practical nuances of pairs trading in different markets and time periods. For instance, \cite{Chen2019} reported large abnormal returns driven by short-term reversals and pairs momentum effects, while \cite{Do2010} showed that simple pairs trading remains viable in turbulent periods despite a general profitability decline in later years. In a UK-centric study, \cite{Bowen2014} recorded moderate annual returns once risk and liquidity were accounted for. Large-scale assessments in \cite{Krauss2016} and \cite{Rad2016} confirmed that distance, cointegration, and copula-based strategies can yield significant alpha but exhibit important differences regarding convergence speed and trading frequencies.
%
%\paragraph{Didactic Sources.}
%Practical guidance and pedagogical discussions on pairs trading can be found in \cite{hudsonthames2024}, which provides a broad compendium of methods, from classical cointegration to machine learning-based selection. In a related vein, \cite{alexander2008market} offers a detailed overview of cointegration techniques in Chapter~II.5 and introduces fundamental principles of copula modeling for financial applications in Chapter~II.6, thus serving as an essential reference for new entrants to the field.
%
%\paragraph{Copula-Based Pairs Trading.}
%An evidently growing strand of research leverages copulas to model more general dependencies beyond linear correlation. Early foundational methods include \cite{Min2010}, which highlights Bayesian pair-copula constructions, and \cite{stander2013trading}, offering a copula-based approach for detecting relative mispricing but noting potential challenges posed by transaction costs. Extensions in \cite{Liew2013} and \cite{Xie2016} underscore that copulas outperform distance-of-prices rules in capturing tail dependencies. Multi-dimensional variants have been proposed (e.g., \cite{lau2016multi}) to incorporate three or more assets into a single framework. Further refinements, like those introduced in \cite{Krauss2017} and \cite{zhi2017dynamic}, combine t-copulas or dynamic copula-GARCH models with individualized thresholds for improved risk-adjusted returns. In the high-frequency domain, \cite{Chu2018} showed that copula-based mispricing indices can be coupled with deep learning for profitability enhancements. Recent efforts also explore mixed copulas (\cite{SabinodaSilva2023}), ARMA-GARCH approaches (\cite{Wang2023}), and copulas specialized for cointegrated assets (\cite{He2024}), culminating in improved alpha extraction. Finally, \cite{Tadi2025} proposes reference-asset-based copula trading specifically for cryptocurrencies, aligning well with the expanding scope of digital assets.
%
%\paragraph{Pairs Trading: Other Approaches.}
%Beyond cointegration or copula methodologies, several innovative techniques have surfaced. New approaches to modeling and parameter estimation for pairs trading appear in \cite{do2006new} and \cite{Zeng2014}, with the latter introducing threshold-based mean-reversion strategies. In more recent research, \cite{Sarmento2020} incorporates machine learning (OPTICS clustering) to constrain search space, while \cite{Johansson2024} leverages convex-concave optimization for multi-asset statistical arbitrage. Reinforcement learning is featured in \cite{Han2023} for automated pair selection, and \cite{qureshi2024pairs} employs a graphical matching approach to reduce overlap among chosen pairs. Further, \cite{Roychoudhury2023} couples clustering with deep RL for equity indices, whereas \cite{Rotondi2025} applies a partial correlation-based distance to cluster promising trading candidates.
%
%\paragraph{Synthetic Controls / Index-Tracking.}
%The method of replicating a target asset's returns by constructing a portfolio of contributor assets is reminiscent of index-tracking procedures. Classic treatments connecting cointegration analysis and hedging tasks (e.g., \cite{Alexander1999} and \cite{Alexander2002}) lay theoretical groundwork for such an approach. Subsequent refinements in \cite{Alexander2005a} and \cite{Alexander2005b} investigate how cointegration outperforms traditional techniques in crafting robust index trackers and exploiting time-varying market regimes. Complementary research (e.g., \cite{Shu2020}) shows that sparse solutions across a large universe can reduce transaction costs, an idea further corroborated in \cite{Bradrania2021}, where machine learning identifies dynamic selection methods for index constituents. These frameworks illustrate how synthetic control concepts provide a flexible foundation for building market-neutral positions or tracking assets with fewer assumptions.